### 2013-08-28 Forensics_Work.tex
Inicial

\documentclass[12pt,twoside,a4paper]{article}
\usepackage[brazil]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{timbre-ic}
\usepackage{booktabs}
\usepackage[table]{xcolor}
\usepackage{url}
\usepackage{array}

\begin{document}

\vskip 15mm

\begin{center} 
\textbf{Projeto de Conclusão de Curso: MO447 - Análise de Impressoras}
\end{center}

\vskip 5mm

\textbf{Aluno:} Adriano Ricardo Ruggero

\textbf{Aluno:} Marião Mestre

\textbf{Aluno:} Gabriel, o Pensador

\textbf{Aluno:} Maurício é de Matar

\vskip 20mm

\begin{abstract}

Aqui a gente coloca o resumo...

\end{abstract}

% resetando configs de layout
\newpage
\pagestyle{plain}
\headheight 0.0cm
\headsep 0.0cm
\footskip 2.2cm

\section{Introdução e justificativa}
\label{sec:introduction}

Aqui nós damos uma pequena introdução no pessoal...

\section{Trabalhos relacionados}
\label{sec:related}

Apresentação de trabalhos relacionados (bibliografia pesquisada).

\section{Objetivos}
\label{sec:objects}

Qual o nosso objetivo? Viver \textit{forever}?

\section{Plano de trabalho}
\label{sec:plan}

Rapaz, o plano é o seguinte:

\section{Materiais e métodos}
\label{sec:materials}

Cumé qui nóis fez?

\section{Conclusões}
\label{sec:conclusions}

Assim sendo, concluímos que blá, blá, blá...

\bibliography{Biblio}{}
\bibliographystyle{acm}

Aqui aparecerão as referências geradas au-to-ma-ti-ca-men-te!!!! (Ohhhhh!!!)

\end{document}

### 2013-08-29 Forensics_Work.tex
Update Forensics_Work.tex
Update teste
Update teste 2
Biblio e Tex update

@@
 \begin{center} 
-\textbf{Projeto de Conclusão de Curso: MO447 - Análise de Impressoras}
+\textbf{Projeto da Disciplina MO447 - Análise Forense de Impressoras}
+
 \end{center}
@@
 
-Apresentação de trabalhos relacionados (bibliografia pesquisada).
+Apresentação de trabalhos relacionados (bibliografia pesquisada).	O \textit{teacher} just gave us two...
+\textit{For instance...}, no trabalho apresentando por José da Silva, em \cite{Bulan} é apresentada a historieta de João e o pé de feijão.
+Em \cite{Kee}, sabemos de Maria enfrentando a bruxa malvada, como o autor quer que acreditemos.
 

### 2013-09-03 2013-mo447-practical-assignment-model.tex
Modelo de artigo

%%% PREAMBLE - Do not touch %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,twocolumn,letterpaper]{article}
\usepackage[ansinew]{inputenc}
\usepackage[portuges,brazil,english]{babel}
\usepackage{model}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{color}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\input{pics/abaco}

\cvprfinalcopy % *** Uncomment this line for the final submission
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}
\ifcvprfinal\pagestyle{empty}\fi

\newcommand{\TODO}[1]{TODO: #1}
\newcommand{\CITEONE}[2]{\mbox{#1 \cite{#2}}}
\newcommand{\CITETWO}[3]{\mbox{#1 and #2 \cite{#3}}}
\newcommand{\CITEN}[2]{\mbox{#1 et al. \cite{#2}}}

%%% Paper beginning %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Here goes the paper title}
\author{Fulano da Silva\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{fulano@ic.unicamp.br}}\\
Fulano da Silva\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{fulano@ic.unicamp.br}}\\
Anderson Rocha\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
}

%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\maketitle
\begin{abstract}
Here goes the abstract. 
\end{abstract}

%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Here goes the introduction and motivation of the work.

Some directions for the paper:

\begin{itemize}
	\item Diagrams and figures are encouraged for making the paper richer
	\item The sections proposed here are not hard-constrained. It means, you 
	can propose other sections as well as change the existing ones. 
\end{itemize}

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State-of-the-Art}
Here goes the state-of-the-art research (talk about prior work for solving the same problem).

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Solution}
Talk about the proposed solution for the selected problem.

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Discussion}
Talk about the experiments carried out and the obtained results.

Examples of citations~\cite{Ni_2008, Ni_2009}. For direct citations use something like:

\CITEONE{Silva}{Silva_2010} for papers with one author.
\CITETWO{Silva}{Souza}{Silva_2010b} for papers with two authors.
\CITEN{Silva}{Silva_2010c} for papers with three or more authors.

Example of a figure of one column. 
\begin{figure}
\begin{center}
	\includegraphics[width=0.99\columnwidth]{pics/example-figure}
	\caption{A figure example spanning one column only.\label{fig:label}}   
\end{center} 
\end{figure}

Example of a figure spanning two columns. 
\begin{figure*}
\begin{center}
	\includegraphics[width=0.99\textwidth]{pics/example-figure-spanned}
	\caption{A figure example spanning two columns.\label{fig:label2}}   
\end{center} 
\end{figure*}

Example of a table spanning only one column:

\begin{table}
\begin{center}
\begin{tabular}{l*{6}{c}r}
Team              & P & W & D & L & F  & A & Pts \\
\hline
Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
FC Copenhagen     & 6 & 2 & 1 & 2 &  5 & 8 &  7  \\
\end{tabular}
\end{center}
\end{table}

Example of a table spanning two columns:

\begin{table*}
\begin{center}
    \begin{tabular}{ | l | l | l | p{8cm} |}
    \hline
    Day & Min Temp & Max Temp & Summary \\ \hline
    Monday & 11C & 22C & A clear day with lots of sunshine.  
    However, the strong breeze will bring down the temperatures. \\ \hline
    Tuesday & 9C & 19C & Cloudy with rain, across many northern regions. Clear spells
    across most of Scotland and Northern Ireland,
    but rain reaching the far northwest. \\ \hline
    Wednesday & 10C & 21C & Rain will still linger for the morning.
    Conditions will improve by early afternoon and continue
    throughout the evening. \\
    \hline
    \end{tabular}
\end{center}    
\end{table*}

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
Present the main conclusions of the work as well as some future directions for other people interested in continuing this work.

%%% References %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\small
\bibliographystyle{unsrt}
\bibliography{references}
}

\end{document}

### 2013-09-30 Paper_presentation.tex
First

\documentclass[notes]{beamer}
\usepackage{graphicx}
\usepackage{url}
\usepackage[english, portuguese]{babel}
\usepackage[latin1, utf8]{inputenc}
\usepackage{times}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\mode<presentation>

{
  % A tip: pick a theme you like first, and THEN modify the color theme, and then add math content.
  % Warsaw is the theme selected by default in Beamer's installation sample files.

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% THEME
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
% \usetheme{Boadilla}
%\usetheme{boxes}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
 \usetheme{default}
% \usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Madrid}
% \usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% COLOR THEME
  %\usecolortheme{albatross}
  %\usecolortheme{beetle}
  %\usecolortheme{crane}
  %\usecolortheme{default}
  %\usecolortheme{dolphin}
  %\usecolortheme{dove}
  %\usecolortheme{fly}
  %\usecolortheme{lily}
  \usecolortheme{orchid}
  %\usecolortheme{rose}
  %\usecolortheme{seagull}
  %\usecolortheme{seahorse}
  %\usecolortheme{sidebartab}
  %\usecolortheme{structure}
  %\usecolortheme{whale}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% OUTER THEME
  %\useoutertheme{default}
  %\useoutertheme{infolines}
  %\useoutertheme{miniframes}
  %\useoutertheme{shadow}
  %\useoutertheme{sidebar}
  %\useoutertheme{smoothbars}
  %\useoutertheme{smoothtree}
  %\useoutertheme{split}
  %\useoutertheme{tree}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%% INNER THEME
  %\useinnertheme{circles}
  %\useinnertheme{default}
  %\useinnertheme{inmargin}
  %\useinnertheme{rectangles}
  %\useinnertheme{rounded}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

  \setbeamercovered{transparent} % or whatever (possibly just delete it)
  % To change behavior of \uncover from graying out to totally invisible, can change \setbeamercovered to invisible instead of transparent. apparently there are also 'dynamic' modes that make the amount of graying depend on how long it'll take until the thing is uncovered.

}

% Get rid of nav bar
\beamertemplatenavigationsymbolsempty

% Use short top
\usepackage[headheight=12pt,footheight=12pt]{beamerthemeboxes}
%\addheadboxtemplate{\color{black}}{
%\hskip0.3cm
%\color{white}
\insertshortauthor
%\insertframenumber \ \ \ \ \ \ \ 
%\insertsection \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \  \insertsubsection
%\hskip0.3cm}
%\addheadboxtemplate{\color{black}}{
%\color{white}
%\ \ \ \ 
%\insertsection
%}
%\addheadboxtemplate{\color{black}}{
%\color{white}
%\ \ \ \ 
%\insertsubsection
%}
\title{Measurement and Analysis of Child Pornography Trafficking on P2P Networks}
\subtitle{}

\institute{Instituto de Computação - Unicamp}

\date{\today}

\subject{Talks}

\def\defn#1{{\color{red} #1}}
% Insert frame number at bottom of the page.
%\setbeamertemplate{footline}[frame number]
\setbeamertemplate{footline}[text line]{%
  \parbox{\linewidth}{\vspace*{-8pt}IC - Instituto de Computação\hfill\inserttitle\hfill\insertpagenumber}}
\setbeamertemplate{navigation symbols}{}

\author{Ryan Hurley, Swagatika Prusty, Hamed Soroush, Robert J. Walls
Jeannie Albrecht, Emmanuel Cecchet, Brian Neil Levine
Marc Liberatore, Brian Lynn, Janis Wolak}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}
  \frametitle{Scheduling}
  \tableofcontents
\end{frame}

\section{Introduction}
\begin{frame}

\end{frame}

%%%%% Thanks page
\begin{frame}
\frametitle{Thanks}
\vskip20pt

\begin{center}
{\bf \color{alert} Thanks!}
\end{center}

\vskip20pt

\begin{center}

\vskip12pt
\end{center}

\titlepage
\end{frame}

\end{document}

### 2013-10-03 Paper_presentation.tex
03_10 02

@@
 \def\defn#1{{\color{red} #1}}
-% Insert frame number at bottom of the page.
-%\setbeamertemplate{footline}[frame number]
+% Insere o numero da pagina no rodape.
 \setbeamertemplate{footline}[text line]{%
@@
 \section{Introduction} 
-\begin{frame}
+%este é um slide de exemplo
+\begin{frame} %começa um novo slide (frame)
+
+\begin{block}{Bloco}
+
+%começa um novo bloco (caixa no slide)
+
+O que eu escrever aqui aparece no bloco.
+
+\end{block} %finaliza o bloco
+
+\begin{block}{Outro bloco}
+
+Posso criar vários blocos em um \textit{frame}...
+E fazer com que apareçam um de cada vez...
+
+\end{block} \pause %o comando "\pause" insere uma pausa no slide
+
+\begin{block}{Bloco oculto}
+
+Este bloco só vai aparecer quando eu "clicar" ou pressionar uma tecla.
+
+\end{block}
 

### 2013-10-14 Paper_presentation.tex
03_10 03
Novo rodapé
Itemização
Inserido Headnote
Criminal Investigation

@@
 %}
-\title{Measurement and Analysis of Child Pornography Trafficking on P2P Networks}
+\title{Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}}
 \subtitle{}
+
+\def\logounicamp{%
+\resizebox{!}{7.5ex}{\includegraphics{unicamp.pdf}}
+}
+
+\def\logoabaco{%
+\resizebox{!}{7.5ex}{\includegraphics{abaco.pdf}}
+}
 
@@
 % Insere o numero da pagina no rodape.
+
+\setbeamertemplate{headline}[text line]{%
+  \parbox{\linewidth}{\vspace*{8pt}\hfill\insertsection}}
+
 \setbeamertemplate{footline}[text line]{%
-  \parbox{\linewidth}{\vspace*{-8pt}IC - Instituto de Computação\hfill\inserttitle\hfill\insertpagenumber}}
+  \parbox{\linewidth}{\vspace*{-8pt}\logounicamp\hfill\institute\hfill\inserttitle
+  \hfill\logoabaco\hfill\insertpagenumber}}
 \setbeamertemplate{navigation symbols}{}
@@
 
+\section{Criminal Investigation}
+\begin{frame}{Slide com \textit{bullets}}
+
+\begin{itemize} 
+    \item[\checkmark] Works properly and is evaluated under the goal of the investigations.
+    \item[\checkmark] We follow that principles, (basic principles) rather than isolated characterization of the users.
+    \item[\checkmark] We wil review the USA\footnote{Fourth Amendment and related jurisprudence} Law under the constraints of criminal investigations for Children Pornograph.
+\end{itemize}
+
+\end{frame}
+
+\section{References}
+\begin{frame} %%[allowframebreaks]
+
+\frametitle{Bibliography}
+
+\bibliographystyle{unsrt}
+\bibliography{refs}
+
+\end{frame}
+
 %%%%% Thanks page

### 2013-10-14 Paper_presentation.tex
Sections added
More content...

@@
 
-\begin{block}{Bloco}
+\end{frame}
 
-%começa um novo bloco (caixa no slide)
+\section{Criminal Investigation}
+\begin{frame}
 
-O que eu escrever aqui aparece no bloco.
+\begin{itemize} 
+    \item[\checkmark] Works properly and is evaluated under the goal of the investigations.
 
-\end{block} %finaliza o bloco
+    \item[\checkmark] We follow that principles, (basic principles) rather than isolated characterization of the users.
 
-\begin{block}{Outro bloco}
+    \item[\checkmark] We will review the USA\footnote{Fourth Amendment and related jurisprudence} Law under the constraints of criminal investigations for Children Pornograph.
+\end{itemize}
 
-Posso criar vários blocos em um \textit{frame}...
-E fazer com que apareçam um de cada vez...
+\end{frame}
 
-\end{block} \pause %o comando "\pause" insere uma pausa no slide
+\begin{frame}
+\begin{block}{Works properly and is evaluated under the goal of the investigations}
 
-\begin{block}{Bloco oculto}
+\begin{itemize}
 
-Este bloco só vai aparecer quando eu "clicar" ou pressionar uma tecla.
+\item[\checkmark]That  means: The criminal investigation is increasingly advanced and with more development tools for this one.
+
+\item[\checkmark]There are always more groups that works to find and to discover and try to prevent Child Pornography (CP).
+
+\item[\checkmark]But it is very difficult do prevent, because of the large scale growth in the worldwide web. There are over 1,8 milion CP in internet ''found on eMule'' (we estimate much more).
+
+\end{itemize}
 
@@
 
-\section{Criminal Investigation}
-\begin{frame}{Slide com \textit{bullets}}
+\begin{frame}
+\begin{block}{Basic principles rather than isolated characterization of the users}
 
 \begin{itemize}
-    \item[\checkmark] Works properly and is evaluated under the goal of the investigations.
-    \item[\checkmark] We follow that principles, (basic principles) rather than isolated characterization of the users.
-    \item[\checkmark] We wil review the USA\footnote{Fourth Amendment and related jurisprudence} Law under the constraints of criminal investigations for Children Pornograph.
+
+\item[\checkmark]This means that we will not discuss about a particular user, but the market situation that involves this type of crime.
+
+\item[\checkmark]In criminal investigations of the type we consider search warrants must specify this location, and not a person (not a user).
+
+\item[\checkmark]Actions by the investigators are shortened by law ''Fourth Amendment and Related Jurisprudence'', where this means that the user has a protection on a electronic data.
+
 \end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+\begin{block}{What is wrong with Fourth Amendment Jurisprudence?}
+
+\textbf{The Third Party Doctrine}
+
+According to the Supreme Court's third party doctrine, personal information, once exposed to any third party, loses all Fourth Amendment protection.
+Some information exposed to third parties is protected by various statutes, but those can be inconsistent and outdated.
+The Electronic Communications Privacy Act (ECPA), for example, is notably out of date, leaving privacy protection of technology, as the Ninth Circuit put it, ''a confusing and uncertain area of the law.''.
+Some privacy interests that are currently unprotected under the Fourth Amendment.
+Konop ...
+also receive protection under the First Amendment – but that protection is far from comprehensive...
+(1967)
+
+\end{block}
+
+\end{frame}
+
+\section{Forensic Measurement}
+\begin{frame}
+
+\end{frame}
+
+\section{Availability and Resilience}
+\begin{frame}
+
+\end{frame}
+
+\section{FOI Redundancy and Availability}
+\begin{frame}
+
+\end{frame}
+
+\section{Comparing Aggressive Peers}
+\begin{frame}
+
+\end{frame}
+
+\section{Analysis of User Aliasing}
+\begin{frame}
+
+\end{frame}
+
+\section{Measurement Limitations}
+\begin{frame}
+
+\end{frame}
+
+\section{Related Work}
+\begin{frame}
+
+\end{frame}
+
+\section{Conclusions and Future Work}
+\begin{frame}
 

### 2013-10-14 Paper_presentation.tex
Table...

@@
 
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]The goal of the pre-warrant phase is not to make an arrest (a user, for example), but it is to obtain a judicially issued search warrant, for such cause (CP).
+
+\item[\checkmark]This means, that we will look for a specify location, and not a person.
+
+\item[\checkmark]Arrests in these criminal cases are typically not based on the network-acquired evidence.
+They are based on the fruits of the search and the person identified as possessing the contraband materials.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]Finally, we note that this follows a forensics model and
+not the traditional security attacker model.
+
+\item[\checkmark]The techniques can be applied very successfully even though there exist many ways to defeat them.
+
+\item[\checkmark]But many people do not attempt to hide them, only change the name of the file, as we know to hide the word ''sexually'', but a intentionally name to be ease to discover the file for another peer.
+
+\end{itemize}
+
+\end{frame}
+
 \section{Forensic Measurement}
@@
 \begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]We know that the strategies for removing content from the entire ecosystem (the internet) must target offenders from all countries.
+
+\item[\checkmark]We do not have of a unified effort, and no such collaboration exists.
+
+\item[\checkmark]Investigators need a triage strategy.
+
+\item[\checkmark]The better were if the investigators have target to catch the more dangerous criminals, but such information is not available.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]In lieu of that ideal, investigators can take peers that are offensive in the net.
+
+\item[\checkmark]Peers that show evidence the target of the intent the user.
+
+\item[\checkmark]This includes peers that are online for the longest duration.
+
+\item[\checkmark]Peers that share the largest number of ''FOI'' (File of Interest).
+
+\item[\checkmark]Offenders by P2P network, as we know: eMule, Gnutella...or offender that seek to escape detection with the use of TOR.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{There are 6 (six) sub-groups of peers offenders:}
+
+\begin{enumerate}
+
+\item The top 10\% of GUID’s of largest corpora.
+
+\item The top 10\% of GUID’s of sharing FOI the most numbers of days.
+
+\item The top 10\% of GUID’s ranked contribuition metric (the same we saw in last topics).
+
+\item The top 10\% of the set of GUID’s linked by ip adress sharing FOI.
+
+\item The top 10\% of GUID’s that use a know TOR exit node.
+
+\item The top 10\% of GUID’s  sharing FOI that use a IP adrres and we infer that is a non TOR relay.
+
+\end{enumerate}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+\begin{block}{We can see this  result under the table:}
+
+\begin{table}
+
+\centering
+
+\caption{Sizes of each GUID subgroup}
+
+\begin{tabular}{ccc}
+
+\hline
+
+Identifier & Gnutella & eMule \\
+
+\hline
+\hline
+All GUIDs & 775,941 & 1,895,804 \\
+Multi-Networks GUIDs & 84,925 (11\%) & 147,904 (7,8\%) \\
+TOR GUIDs & 3,666 (0.47\%) & 16,290 (0.86\%) \\
+TOR GUIDs (>2 days) & 2,592 (0.33\%) & 11,998 (0.63\%) \\
+Relayed GUIDs & 76,478 (9.9\%) & 78,223 (4.1\%) \\
+Top 10\% Observed & 84,235 (11\%) & 190,797 (10\%) \\
+Top 10\% by Corpus & 77,782 (10\%) & 189,951 (10\%) \\
+Top 10\% by Contribution & 77,595 (10\%) & 189,581 (10\%)\\
+
+\hline
+\end{tabular}
+\label{table2}
+\end{table}
+
+\end{block}
 

### 2013-10-14 Paper_presentation.tex
Table 3
Parte do Mestre finalizada e Agenda

@@
 Marc Liberatore, Brian Lynn, Janis Wolak}
+
+\AtBeginSection[]{%
+  \begin{frame}
+    \frametitle{Schedule}
+    \tableofcontents[currentsection]
+  \end{frame}
+  \addtocounter{framenumber}{-1}% If you don't want them to affect the slide number
+}
 
@@
 \begin{frame}
-\begin{block}{We can see this  result under the table:}
+\begin{block}{We can see this result under the tables:}
 
@@
 
-\begin{tabular}{ccc}
+\begin{tabular}{ccc}\hline & \multicolumn{2}{c}{Network} \\
 
@@
 \label{table2}
+
 \end{table}
@@
 \end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}
+
+\begin{table}
+
+\centering
+
+\caption{Numbers of IP addresses per network sharing FOI}
+
+\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\
+
+\hline
+
+Network & Total & Private & TOR \\
+
+\hline
+\hline
+Gnutella & 3,025,530 & 32,195 & 7,357 \\
+eMule & 5,643,350 & 1,256 & 21,025 \\
+Ares & 1,714,894 & 225 & 1,799 \\
+IRC & 88,658 & 245 & 746 \\
+
+\hline
+
+\end{tabular}
+\label{table3}
+
+\end{table}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]The differences of each subgroup to the set of all GUIDs are significant (p < 0.001).
+
+\item[\checkmark]Below we provide characteristics of each subgroup, and details of the behavior of each.
+
+\item[\checkmark]For example, we show that GUIDs using TOR to share FOI use it irregularly, and therefore their true IP addresses are easily identifiable.
+
+\end{itemize}
 

### 2013-10-14 Paper_presentation.tex
Agora com tabelas corretamente numeradas
Contribuindo...

@@
 \usepackage{fancyhdr}
+\setbeamertemplate{caption}[numbered]
 \mode<presentation>
@@
 
+\addto\captionsportuguese{
+\renewcommand{\figurename}{Figure}
+\renewcommand{\tablename}{Table}
+}
+
 \begin{document}
@@
 
+\begin{itemize}
+
+\item[\checkmark] This study is based upon the analysis of a large number of observations of CP files on P2P networks.
+
+\item[\checkmark] Also based upon the behavior of the peers that share these files.
+
+\item[\checkmark] Most previous studies of P2P networks have taken place over just several days, or weeks, or a few months.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark] This study is comprises of a thousand of observations per day for a full year.
+
+\item[\checkmark] This duration is specially critical in criminal investigations.
+
+\item[\checkmark] Scientific studies of crimes are often submitted as supporting facts during trial and sentencing.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark] This study focus is on \textit{files of interest} (FOI).
+
+\item[\checkmark] These files includes child pornography (CP) images, as well as stories, child erotica and collections associated with this kind of crimes.
+
+\item[\checkmark] Only content with hashing values matching a list put together by law enforcement by visual inspection was logged.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+\begin{block}{Background}
+
+\begin{itemize}
+
+\item[\checkmark]This paper is based on data collected with the help of national and international law enforcement.
+
+\item[\checkmark]Starting in January 2009, they began deploying a set of forensics tools for online investigations.
+
+\item[\checkmark]Prior to these collaborative efforts, the standard method for online investigation of CP was to make isolated cases.
+
+\item[\checkmark]Leads were not shared among agencies or offices, other than by phone or e-mail.
+
+\item[\checkmark]Officers leverage their own experience to prioritize suspects.
+
+\end{itemize}
+
+\end{block}
+
 \end{frame}
@@
 
-\begin{table}
-
+\begin{table}[H]
 \centering
@@
 \caption{Sizes of each GUID subgroup} 
-
+\label{tab:table2}
 \begin{tabular}{ccc}\hline & \multicolumn{2}{c}{Network} \\
@@
 \end{tabular}
-\label{table2}
 
@@
 \caption{Numbers of IP addresses per network sharing FOI} 
-
+\label{tab:table3}
 \begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\
@@
 \end{tabular}
-\label{table3}
 

### 2013-10-15 Paper_presentation.tex
Mais um pouco...
Dia do Professor
Adicionada parte do Maurício Kubrusly

@@
 
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Background}
+
+\begin{itemize}
+
 \item[\checkmark]Prior to these collaborative efforts, the standard method for online investigation of CP was to make isolated cases.
@@
 
+\begin{frame}
+
+\begin{block}{Tools}
+
+\begin{itemize}
+
+\item[\checkmark]A suite of tools, called \textit{RoundUp}\footnote{Strengthening forensic investigations of child pornography on P2P networks\cite{Liberatore}} (deployed by the researchers) has enabled sharing of plain view observations of online CP and associated activities on various networks.
+
+\item[\checkmark]
+
+\item[\checkmark]
+
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
 \section{Availability and Resilience}
 \begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]Law enforcement’s limited resources and time.
+
+\item[\checkmark]Need triage, focusing on greater impact.
+
+\item[\checkmark]Goal: Decrease the availability of FOI.
+
+\end{itemize}
 
@@
 \begin{frame}
+
+\begin{block}{File Redundancy Across GUIDs}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.5]{FOI_redundancy}
+\caption{Count of how many IDs are sharing the same file}.
+\label{fig:FOI_redundancy}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{File Redudancy Across GUIDs}
+
+\begin{itemize}
+
+\item[\checkmark]Low redudancy of FOIs across the GUIDs:
+	\begin{itemize}
+
+	\item 90\% of Gnutella files, shared by at most 20 Ids.
+
+	\end{itemize}
+
+\item[\checkmark]Files in common between networks have more redudancy.
+
+\item[\checkmark]Apparently, a good strategy would be to prioritize the users with less redundant FOI.
+
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{File Availability Across Days}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.5]{FOI_availability}
+\caption{Count of days a file has been found online}.
+\label{fig:FOI_availability}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{File Availability Across Days}
+
+\begin{itemize}
+
+\item[\checkmark]Gnutella have a lower availability than eMule:
+
+	\begin{itemize}
+
+	\item Only 30\% of Gnutella files are available more than 10 days	.
+
+	\end{itemize}
+
+\item[\checkmark]Files available fewer days, tend to be also less redundant.
+
+\item[\checkmark]Common files also have a greater availability.
+
+\end{itemize}
+
+\end{block}
 
@@
 \label{tab:table3}
-\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\
+\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Addresses} \\
 
@@
 
+\begin{itemize}
+
+\item[\checkmark]Files in U.S mainly. Others countries are underestimated.
+
+\item[\checkmark]No total coverage of files of a certain GUID.
+
+\item[\checkmark]Peers that are rarely online or have few files may have been missed.
+
+\item[\checkmark]Greater number of GUIDs because of different installations.
+
+\item[\checkmark]Peers may have been removed because of police action.
+
+\end{itemize}
+
 \end{frame}
@@
 \begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]Ecosystems and Underground Economies:
+
+	\begin{itemize}
+
+	\item Economic characteristics of Network-based ecosystems.
+
+	\item May explain the irregular use of Tor encountered.
+
+	\end{itemize}
+
+\item[\checkmark]Content Availability in P2P Systems:
+
+	\begin{itemize}
+
+	\item Research of general use of P2P.
+
+	\end{itemize}
+
+\item[\checkmark]CP Trafficking in P2P Systems:
+
+	\begin{itemize}
+
+	\item Previous work are shallow on understanding how these files are being shared.
+
+	\end{itemize}
+
+\end{itemize}
 

### 2013-10-15 Paper_presentation.tex
Tabela redimensionada

@@
 
-\item[\checkmark]
+\item[\checkmark]The shared data provide each investigator with a view of CP offenders and a method of triage for selecting targets  (and enable this study).
 
-\item[\checkmark]
+\item[\checkmark]The tools are still in use, and law enforcement execute approximately 150 search warrants nationwide per month.
 
 \end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Datasets}
+
+\begin{table}[H]
+\begin{small} 
+\setlength{\tabcolsep}{0.1pt} 
+\centering
+
+\caption{Datasets} 
+\label{tab:table1}
+\begin{tabular}{|c|c|c|c|c|}\hline \\
+
+\hline
+
+Network & Data Range & Files & GUIDs & Records \\
+
+\hline
+\hline
+Gnutella (FOI only) & 10/1/2010–9/18/2011 & 139,604 & 775,941 & 870,134,671 \\
+Gnutella Browse & 6/1/2009–9/18/2011 & 87,506,518 & 570,206 & 434,849,112 \\
+eMule (FOI only) & 10/1/2010–9/18/2011 & 29,458 & 1,895,804 & 133,925,130 \\
+IRC (no file data) & 6/2/2011–9/18/2011 & N/A & N/A & 7,272,739 \\
+Ares (no file data) & 5/31/2011–9/18/2011 & N/A & N/A & 17,706,744\\
+
+\hline
+\end{tabular}
+\end{small}
+\end{table}
 

### 2013-10-15 Paper_presentation.tex
Novas imagens

@@
 
+\begin{frame}
+
+\begin{block}{Other details}
+
+\begin{itemize}
+
+\item[\checkmark]Gnutella allows a peer to be browsed, so investigators can enumerate all files shared.
+
+\item[\checkmark]Gnutella Browse dataset consists peer browses, not just FOI, but some Gnutella peers cannot be browsed (client configuration).
+
+\item[\checkmark]eMule does not permit browses, so each of these datasets includes only peers that share FOIs;
+
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Other details}
+
+\begin{itemize}
+
+\item[\checkmark]A GUID’s library is the set of files that were observed being shared by that GUID on a given day.
+
+\item[\checkmark]A GUID’s corpus is the set of all files shared by that GUID over the entire duration of the study.
+
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
 \section{Availability and Resilience}
@@
 
+\begin{frame}
+
+\begin{block}{A comparison of Peer Behavior}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.35]{CDF_characterization_emule}
+\caption{Cumulative distribution function (eMule)}.
+\label{fig:CDF_characterization_emule}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{A comparison of Peer Behavior}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.35]{CDF_characterization_gnutella}
+\caption{Cumulative distribution function (Gnutella)}.
+\label{fig:CDF_characterization_gnutella}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
 \section{Analysis of User Aliasing}

### 2013-10-15 Paper_presentation.tex
Multirow

@@
 \usepackage{times}
+\usepackage{multirow}
 \usepackage[T1]{fontenc}
@@
 
+\begin{frame}
+
+\begin{block}
+
+\begin{table}
+
+\centering
+
+\caption{Characterization of GUIDs groups} 
+\label{tab:table4}
+\begin{tabular}{c|ccc}\hline & \multicolumn{1}{c}{GUID Groups} & \multicolumn{2}{c}{Mean Value (99\% CI)} \\
+
+\hline 
+& & Corpus Size & Days Observed \\
+
+\hline
+\hline
+\parbox[t]{2mm}{\multirow{6}{*}{\rotatebox[origin=c]{90}{Gnutella}}} & All & 10.9 (10.7, 11.1) & 5.2 (5.2, 5.2) \\
+& TOR & 43.9 (39.0, 49.6) & 23.4 (21.8, 25.1)\\
+& Relayed & 18.9 (18.3, 19.5) & 4.8 (4.7, 4.9)\\
+& Multi-Network & 25.9 (24.9, 27.0) & 10.8 (10.6, 11.0)\\
+& Top 10\% Obs. & 41.8 (40.7, 43.0) & 28.7 (28.5, 29.0)\\
+& Top 10\% Corp. & 75.9 (74.3, 77.7) & 16.2 (16.0, 16.5)\\
+& Top 10\% Contr. & 69.1 (67.6, 70.9) & 19.5 (19.3, 19.8)\\
+\hline
+
+\end{tabular}
+
+\end{table}
+
+\end{block}
+
+\end{frame}
+
 \section{Analysis of User Aliasing}

### 2013-10-15 Paper_presentation.tex
Rest...
Figuras Libraries

@@
 \centering
-\includegraphics[scale=0.35]{CDF_characterization_emule}
-\caption{Cumulative distribution function (eMule)}.
-\label{fig:CDF_characterization_emule}
+\includegraphics[scale=0.35]{CDF_characterization_gnutella}
+\caption{Cumulative distribution function (Gnutella)}.
+\label{fig:CDF_characterization_gnutella}
 \end{figure}
@@
 \centering
-\includegraphics[scale=0.35]{CDF_characterization_gnutella}
-\caption{Cumulative distribution function (Gnutella)}.
-\label{fig:CDF_characterization_gnutella}
+\includegraphics[scale=0.35]{CDF_characterization_emule}
+\caption{Cumulative distribution function (eMule)}.
+\label{fig:CDF_characterization_emule}
 \end{figure}
@@
 
+\begin{frame}
+
+\begin{block}
+
+\begin{table}
+
+\centering
+
+\caption{Characterization of GUIDs groups} 
+\label{tab:table5}
+\begin{tabular}{c|ccc}\hline & \multicolumn{1}{c}{GUID Groups} & \multicolumn{2}{c}{Mean Value (99\% CI)} \\
+
+\hline 
+& & Corpus Size & Days Observed \\
+
+\hline
+\hline
+\parbox[t]{2mm}{\multirow{6}{*}{\rotatebox[origin=c]{90}{eMule}}} & All & 4.3 (4.3, 4.4) & 4.1 (4.1, 4.1) \\
+& TOR & 21.2 (19.9, 22.5) & 17.4 (16.9, 18.0)\\
+& Relayed & 9.2 (8.9, 9.6) & 5.5 (5.4, 5.6)\\
+& Multi-Network & 10.8 (10.6, 11.0) & 9.5 (9.4, 9.7)\\
+& Top 10\% Obs. & 23.5 (23.2, 23.8) & 22.3 (22.2, 22.4)\\
+& Top 10\% Corp. & 27.8 (27.4, 28.5) & 18.7 (18.6, 18.8)\\
+& Top 10\% Contr. & 25.8 (25.4, 26.5) & 19.0 (18.9, 19.1)\\
+\hline
+
+\end{tabular}
+
+\end{table}
+
+\end{block}
+
+\end{frame}
+
 \section{Analysis of User Aliasing}
 \begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]The relationship between p2p network GUIDs and real users is not one-to-one in the dataset.
+
+\item[\checkmark]A single user may correspond to multiple GUIDs.
+
+\item[\checkmark]This is known as \textit{user aliasing}, and may be intentional.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Reasons for deliberate aliasing can be:}
+
+\begin{itemize}
+
+\item[\checkmark]A user has two computers (or multiple
+accounts on a single computer), each with an installation
+of Gnutella.
+
+\item[\checkmark]A user may reinstall or upgrade their p2p client on a single computer or modify their GUID over time.
+
+\item[\checkmark]
+
+\end{itemize}
+
+\end{block}
 

### 2013-10-15 Paper_presentation.tex
So close...

@@
 
-\item[\checkmark]
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Gnutella unique libraries on specific days}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.3]{Libraries_specific_day}
+\caption{Gnutella unique libraries on specific days}.
+\label{fig:Libraries_specific_day}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]GUIDs with a single file are easily aliased with other GUIDs with the same single file.
+
+\item[\checkmark]About 58\% of GUIDs have unique libraries on a
+given day of the dataset.
 
 \end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]40\% of Gnutella GUIDs that have two or more FOI:
+	\begin{itemize}
+	\item Over 95\% have unique libraries.
+	\end{itemize}
+
+\item[\checkmark]25\% of GUIDs with three or more FOI: 
+	\begin{itemize}
+	\item Over 99\% have distinct libraries.
+	\end{itemize}
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Basicly:}
+
+\begin{itemize}
+
+\item[\checkmark]GUIDs with two or more files in their library had a unique library about 95\% of the time;
+
+\item[\checkmark]GUIDs with three or more files were unique over 99\% of the time.
+
+\end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{These data suggest:}
+
+\begin{itemize}
+
+\item[\checkmark]GUIDs can be treated as uniquely distinguishable when their libraries contain at least two FOI or when are considered all files that they share.
+
+\item[\checkmark] Users are rarely if ever changing their GUID and appearing on the same day with the same library.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Uniquesses of partial and complete libraries using Jaccard index}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.3]{Libraries_unique}
+\caption{Uniquesses of partial and complete libraries using Jaccard index}.
+\label{fig:Libraries_unique}
+\end{figure}
 

### 2013-10-15 Paper_presentation.tex
Só falta o Jaccard
Final (falta Gabriel)

@@
 
-\begin{block}{Basicly:}
+\begin{block}{Basically:}
 
@@
 
-\end{frame}
-
-\begin{frame}
-
-\begin{block}{Uniquesses of partial and complete libraries using Jaccard index}
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Uniquesses of partial and complete libraries using Jaccard index $ J(A,B)=\left| \frac{A\cup B} {A\cap B} \right|$}
 
@@
 \centering
-\includegraphics[scale=0.3]{Libraries_unique}
+\includegraphics[scale=0.25]{Libraries_unique}
 \caption{Uniquesses of partial and complete libraries using Jaccard index}.
@@
 
+\begin{itemize}
+
+\item[\checkmark]Criminal trafficking of CP on p2p networks is
+widespread, with no easy answers for law enforcement looking
+to curtail it.
+
+\item[\checkmark]Triage as a strategy due:
+
+	\begin{itemize}
+
+	\item Diversity in peers’ location.
+	\item Redundancy of the libraries.
+	\item Many p2p networks.
+	\item Limited law enforcement resources.
+
+	\end{itemize}
+
+\item[\checkmark]Investigators should carefully choose peers
+to investigate and remove from p2p networks.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]Naïve approaches to triage are ineffective and optimal approaches are NP-Hard.
+
+\item[\checkmark]Tractable heuristics yield reasonable and useful results.
+
+\item[\checkmark]Use of these heuristics are complemented by the
+discovery of aggressive subgroups of CP traffickers.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{itemize}
+
+\item[\checkmark]No significant evidence of users attempting to hide file libraries.
+
+	\begin{itemize}
+
+	\item Libraries are largely unique, strongly implying a unique user behind each such library.
+
+	\end{itemize}
+
+\item[\checkmark]Some users do use Tor, but most do so inconsistently.
+
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}
+
+\begin{block}
+
+It is an open question as to whether network-observable
+behaviors correlate with off-line behaviors, such as
+child molestation.
+
+\end{block}
+
 \end{frame}
@@
 %%%%% Thanks page
+\section{Thanks}
 \begin{frame}
 \frametitle{Thanks}
-\vskip20pt
+\vskip30pt
 
@@
 
-\vskip20pt
+\vskip30pt
 
@@
 \vskip12pt
+
+Adriano R. Ruggero, Gabriel Rodrigues, Mário F. Brito, Maurício L. Perez
+
 \end{center}
 
-\titlepage
+%%\titlepage
 \end{frame}

### 2013-10-15 Paper_presentation.tex
Parte Gabriel

@@
 \begin{frame} %começa um novo slide (frame)
-
+\begin{block}{Introduction}
+\begin{itemize}
+
+\item[\checkmark] Peer-to-peer (p2p) networks are the most popular mechanism for the criminal acquisition and distribution of child sexual exploitation imagery(CP).
+\item[\checkmark] Observations of peers sharing known CP on the eMule and Gnutella networks.
+\item[\checkmark] Investigating CP trafficking online.
+\item[\checkmark] Two primary goals:
+
+\begin{itemize}
+
+\item Stop the distribution of CP.
+\item Catch child molesters.
+
+\end{itemize}
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}
+\begin{itemize}
+
+\item[\checkmark] Numerous studies of p2p networks have explored the availability, performance, and traffic characteristics of file sharing.
+\item[\checkmark] Triage fundamental problem.
+\item[\checkmark] Key contributions:
+
+\begin{itemize}
+
+\item Removing peers with the largest contributions.
+\item Examine subgroups of agressive peers.
+\item Tor project.
+\item Tools use in all U.S states and result.
+
+\end{itemize}
+\end{itemize}
 \end{frame}
@@
 \end{itemize}
+
+\end{block}
+
+\end{frame}
+
+\begin{frame}
+\begin{block}{Law Enforcement Strategy}
+\begin{itemize}
+
+\item[\checkmark] Investigators have a global, historical view of GUIDs and their corpora, including known FOI and other files. 
+\item[\checkmark] An enormous set of perpetrators are active every day
+around the world.
+\item[\checkmark] Evaluate four greedy heuristics aimed at reducing the availability of CP by removing peers.
+
+\begin{itemize}
+
+\item Removing peers that were observed most often.
+\item Removing peers with the largest corpus size.
+\item Removing peers with the largest contribution to availability.
+\item Removing peers selected randomly, as a baseline.
+
+\end{itemize}
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}
+\begin{block}{Comparison of the Efficiency of heuristic}
+\begin{itemize}
+
+\item[\checkmark] The Figure(Top GUIDs Removed) show a percentage of GUIDs removed according to different
+heuristics:
+
+\begin{itemize}
+
+\item[\checkmark] Random.
+\item[\checkmark] Number of days observed. 
+\item[\checkmark] Corpus size.
+\item[\checkmark] Contribution to file availability on Gnutella and eMule.
+\item[\checkmark] 10 or fewer FOI.
+\item[\checkmark] Peers in the U.S.
+
+\end{itemize}
+\end{itemize}
+\end{block}
+\end{frame}
+\begin{frame}
+
+\begin{block}{Percentage of Top GUIDs Removed}
+\begin{itemize}
+
+\item[\checkmark] Removed the top 0.01, 0.1, 1, and 10 percent of GUIDs according to each heuristic.
+\item[\checkmark] In Gnutella, the Corpus and Contribution heuristics achieve equal results when 0.113 percent of GUIDs are removed. 
+\item[\checkmark] The impact of removing 100 percent of peers with 10 or fewer
+FOI, and 100 percent of peers in the U.S.
+
+\end{itemize}
+\end{block}
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Percentage of Top GUIDs removed}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.5]{Top_GUIDs_Removed}
+\caption{Percentage of Top GUIDs removed}
+\label{fig:Top_GUIDs_Removed}
+\end{figure}
+
+\end{block}
+
+\end{frame}
+
+%-Availability and resilience------------------------------------------------
+
+\begin{frame}
+\begin{block}{Impact of Geography on Availability}
+\begin{itemize}
+\item[\checkmark] The tools and methodologies is based on the U.S.
+law enforcement, and the files they are looking for are arguably tuned to U.S.
+perpetrators.
+Because the law enforcement agents are limited by jurisdiction.
+\item[\checkmark] Only a small majority of top Gnutella GUIDs 57 out of 100 are located in the U.S. Just 30 percent of files are unavailable (internationally) after removing all GUIDs in the U.S.
+\item[\checkmark] Within the U.S., the problem is similarly large in scope. The top 5 percent of GUIDs in the U.S. comprises a set of 14,410 GUIDs, each with a corpus of at least 40 known FOI.
+
+\end{itemize}
+\end{block}
+\end{frame}
+%-Availability and resilience------------------------------------------------
+
+\begin{frame}
+\begin{block}{Impact of Low-Sharing GUIDs on Availability}
+\begin{itemize}
+\item[\checkmark] A large portion of GUIDs have comparatively few files. 
+\item[\checkmark] Reasons peers may appear to have few files.
+\begin{itemize}
+\item[\checkmark] They may be downloading FOI and not subsequently sharing them.
+\item[\checkmark] They may have downloaded the files incidental to other activities.
+\item[\checkmark] They may have downloaded the files incidental to other activities.
+\item[\checkmark] They may simply be sharing a smaller library.
+\end{itemize}
+
+\end{itemize}
+\end{block}
+\end{frame}
+\begin{frame}
+\begin{block}{Files in Corpus}
+\begin{itemize}
+\item[\checkmark] CDF showing the corpus size per GUID.
+\begin{itemize}
+\item[\checkmark] The blue line show all FOI observed in Gnutella.
+\item[\checkmark] The black line (“Gnutella Browse GUIDs”) show the corpus size distribution for all files seen at GUIDs whose libraries were browsed.
+\item[\checkmark] The green line shows the distribution of FOIs within those browses.
+\item[\checkmark] The red line show all FOI observed in eMulle.
+\end{itemize}
+\end{itemize}
+
+\end{block}
+\end{frame}
+
+\begin{frame}
+
+\begin{block}{Files in Corpus}
+
+\begin{figure}[!htb]
+\centering
+\includegraphics[scale=0.5]{Files_in_Corpus}
+\caption{Files in Corpus}
+\label{fig:Files_in_Corpus}
+\end{figure}
 

### 2013-10-15 Paper_presentation.tex
Corrigido .

@@
 \includegraphics[scale=0.5]{FOI_redundancy}
-\caption{Count of how many IDs are sharing the same file}.
+\caption{Count of how many IDs are sharing the same file}
 \label{fig:FOI_redundancy}
@@
 \includegraphics[scale=0.5]{FOI_availability}
-\caption{Count of days a file has been found online}.
+\caption{Count of days a file has been found online}
 \label{fig:FOI_availability}
@@
 \includegraphics[scale=0.35]{CDF_characterization_gnutella}
-\caption{Cumulative distribution function (Gnutella)}.
+\caption{Cumulative distribution function (Gnutella)}
 \label{fig:CDF_characterization_gnutella}
@@
 \includegraphics[scale=0.35]{CDF_characterization_emule}
-\caption{Cumulative distribution function (eMule)}.
+\caption{Cumulative distribution function (eMule)}
 \label{fig:CDF_characterization_emule}
@@
 \includegraphics[scale=0.3]{Libraries_specific_day}
-\caption{Gnutella unique libraries on specific days}.
+\caption{Gnutella unique libraries on specific days}
 \label{fig:Libraries_specific_day}
@@
 \includegraphics[scale=0.25]{Libraries_unique}
-\caption{Uniquesses of partial and complete libraries using Jaccard index}.
+\caption{Uniquesses of partial and complete libraries using Jaccard index}
 \label{fig:Libraries_unique}

### 2013-10-16 Paper_presentation.tex
Corrigido duplicidade

@@
 
-\item[\checkmark] Random.
-\item[\checkmark] Number of days observed. 
-\item[\checkmark] Corpus size.
-\item[\checkmark] Contribution to file availability on Gnutella and eMule.
-\item[\checkmark] 10 or fewer FOI.
-\item[\checkmark] Peers in the U.S.
+\item Random.
+\item Number of days observed. 
+\item Corpus size.
+\item Contribution to file availability on Gnutella and eMule.
+\item 10 or fewer FOI.
+\item Peers in the U.S.
 
@@
 \begin{itemize}
-\item[\checkmark] They may be downloading FOI and not subsequently sharing them.
-\item[\checkmark] They may have downloaded the files incidental to other activities.
-\item[\checkmark] They may have downloaded the files incidental to other activities.
-\item[\checkmark] They may simply be sharing a smaller library.
+\item They may be downloading FOI and not subsequently sharing them.
+\item They may have downloaded the files incidental to other activities.
+\item They may simply be sharing a smaller library.
 \end{itemize}
@@
 \begin{itemize}
-\item[\checkmark] The blue line show all FOI observed in Gnutella.
-\item[\checkmark] The black line (“Gnutella Browse GUIDs”) show the corpus size distribution for all files seen at GUIDs whose libraries were browsed.
-\item[\checkmark] The green line shows the distribution of FOIs within those browses.
-\item[\checkmark] The red line show all FOI observed in eMulle.
+\item The blue line show all FOI observed in Gnutella.
+\item The black line (“Gnutella Browse GUIDs”) show the corpus size distribution for all files seen at GUIDs whose libraries were browsed.
+\item The green line shows the distribution of FOIs within those browses.
+\item The red line show all FOI observed in eMulle.
 \end{itemize}

### 2013-11-17 Printer_Balistics.tex
Inserted final work

--- 2013-09-03 2013-mo447-practical-assignment-model.tex
@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
-\input{pics/abaco}
+\input{abaco}
 
@@
 %%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Here goes the paper title}
-\author{Fulano da Silva\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{fulano@ic.unicamp.br}}\\
-Fulano da Silva\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{fulano@ic.unicamp.br}}\\
+\title{Printer ballistics through gray-level co-occurrence matrix of characters}
+\author{Adriano Ricardo Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
+Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel.rodrigues@aol.com}}\\
 Anderson Rocha\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
@@
 \begin{center}
-	\includegraphics[width=0.99\columnwidth]{pics/example-figure}
+	\includegraphics[width=0.99\columnwidth]{example-figure}
 	\caption{A figure example spanning one column only.\label{fig:label}}   
@@
 \begin{center}
-	\includegraphics[width=0.99\textwidth]{pics/example-figure-spanned}
+	\includegraphics[width=0.99\textwidth]{example-figure-spanned}
 	\caption{A figure example spanning two columns.\label{fig:label2}}   
@@
 \bibliographystyle{unsrt}
-\bibliography{references}
+\bibliography{references_printer}
 }

### 2013-11-17 Printer_Balistics.tex
Editing...

@@
 \documentclass[10pt,twocolumn,letterpaper]{article}
-\usepackage[ansinew]{inputenc}
+%%\usepackage[ansinew]{inputenc}
+\usepackage[latin1,utf8]{inputenc}
 \usepackage[portuges,brazil,english]{babel}
@@
 \title{Printer ballistics through gray-level co-occurrence matrix of characters}
-\author{Adriano Ricardo Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
-Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel.rodrigues@aol.com}}\\
-Anderson Rocha\thanks{Is with the Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
+\author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
+Gabriel Rodrigues\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{gabriel\_rodrigues@aol.com}}\\
+Mário Brito\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
+\tt\small{britomar@aedu.com}}\\
+Maurício Perez\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}:
+\tt\small{mauriciolp84@gmail.com}}\\
+Anderson Rocha\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{anderson.rocha@ic.unicamp.br}}
 }

### 2013-11-17 Printer_Balistics.tex
Editing...

@@
 %%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Printer ballistics through gray-level co-occurrence matrix of characters}
+\title{Printer ballistics through analysis of character's texture}
 \author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
@@
 \begin{abstract}
-Here goes the abstract. 
+We describe a technique for ballistics of printed documents, that is, link a printed document to a especific printer.
+The principle of this technique is the analysis of character's texture, extracting some properties from the characters of printed and scanned documents, and relate this properties through a co-occurence matrix.
+This matrix can be used to create a "fingerprint" of characters (and related printers), that allows identify a specific printer device that print these characters.
 \end{abstract}

### 2013-11-17 Printer_Balistics.tex
Editing...

@@
 \section{Introduction}
-Here goes the introduction and motivation of the work.
+In August of 2013, a russian man wrote his own small print in a credit card contract.
+The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the documents.
+The alterations included unlimited credit line, 0 percent interest rates and no fees.
+When the bank decided to terminate man's credit card, because overdue payments, he sued they for more than 24 million rubles (US\$ 727.000).
+How the bank could prove the falsification?
 
-Some directions for the paper:
-
-\begin{itemize}
-	\item Diagrams and figures are encouraged for making the paper richer
-	\item The sections proposed here are not hard-constrained. It means, you 
-	can propose other sections as well as change the existing ones. 
-\end{itemize}
+Legal aspects aside, a way to verify if a document, or a part of it, came from a specific device can be character's texture analysis.
 

### 2013-11-17 Printer_Ballistics.tex
Printer Ballistics

--- 2013-11-17 Printer_Balistics.tex
@@
 %%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Printer ballistics through analysis of character's texture}
+\title{Printer ballistics through character's texture analysis}
 \author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
@@
 \section{Introduction}
-In August of 2013, a russian man wrote his own small print in a credit card contract.
+In August of 2013, a russian man wrote his own small print in a credit card contract~\cite{RT}.
 The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the documents.
-The alterations included unlimited credit line, 0 percent interest rates and no fees.
+The changes included unlimited credit line, 0 percent interest rates and no fees.
 When the bank decided to terminate man's credit card, because overdue payments, he sued they for more than 24 million rubles (US\$ 727.000).
@@
 
+Altough we are living in a digital era, printed documents still are significant part of our daily.
+Likewise, with the constant reduction in prices and increase in quality of printing equipment, forgeries become increasingly commonplace.
+
 Legal aspects aside, a way to verify if a document, or a part of it, came from a specific device can be character's texture analysis.
+
+Our approach for the analysis of character's texture made up as follows.
+From printed pages scanned at high resolution, selected characters were extracted.
+From these characters, we obtained its properties of contrast, correlation, energy and homogeneity, creating with them an co-occurrence matrix.
+This matrix can be called a ''fingerprint'' of the character.
+This ''fingerprint'' of  characters is closely related to the printing device which originated it, and can be used to identify which printer was responsible for printing it.
+
+However, slight imperfections may occur during the printing and/or scanning process of documents.
+To handle these small errors (or variations), characters were selected from different areas of scanned document, their properties were obtained and then classified using machine learning algorithms.
 

### 2013-11-17 Printer_Ballistics.tex
Printer Ballistics...

@@
 \begin{center}
-\begin{tabular}{l*{6}{c}r}
-Team              & P & W & D & L & F  & A & Pts \\
+\begin{tabular}{l*{2}{c}r}
+Printer           & Documents \\
 \hline
-Manchester United & 6 & 4 & 0 & 2 & 10 & 5 & 12  \\
-Celtic            & 6 & 3 & 0 & 3 &  8 & 9 &  9  \\
-Benfica           & 6 & 2 & 1 & 3 &  7 & 8 &  7  \\
-FC Copenhagen     & 6 & 2 & 1 & 2 &  5 & 8 &  7  \\
+Brother-HL4070CDW & 28 \\
+Canon-D1150 & 28 \\
+Canon-MF3240 & 28 \\
+Canon-MF4370DN & 28 \\
+HP-CLJ-CP2025A & 28 \\
+HP-CLJ-CP2025B & 28 \\
+HP-JL-CP1518 & 28 \\
+Lexmark-E260D & 28 \\
+OKI-C330 & 28 \\
+Samsung-CLP315 & 28 \\
 \end{tabular}

### 2013-11-17 Printer_Ballistics.tex
Solution...

@@
 \section{Proposed Solution}
-Talk about the proposed solution for the selected problem.
+
+Our solution consist in getting the image of characters selected from scanned documents in grayscale, extract its properties of contrast, correlation, energy and homogeneity - creating a co-occurrence matrix - and cluster them by machine learning algorithms.
+
+The characters chosen for this work were "e" and "t", both in lowercase, because they are, respectively, the first and second most common letters in texts written in English~\cite{Letter_Frequency}.
+
+Due to the fact that all scanned documents come from laser printers, it was necessary to take some precautionary measures.
+Laser printers are known as ''page printers'', while dot matrix printers and inkjet printers are called ''line printers''.
+This is a crucial difference, and should be considered for more careful study.
+Line printers print documents line by line from the top of the sheet, keeping a characteristic pattern which periodically repeats for each paper feed.
+That is, any line printed by this printer model will have basically the same characteristics, regardless of their vertical location in the sheet of paper.
 
@@
 \section{Experiments and Discussion}
-Talk about the experiments carried out and the obtained results.
-
-Examples of citations~\cite{Ni_2008, Ni_2009}. For direct citations use something like:
-
-\CITEONE{Silva}{Silva_2010} for papers with one author.
-\CITETWO{Silva}{Souza}{Silva_2010b} for papers with two authors.
-\CITEN{Silva}{Silva_2010c} for papers with three or more authors.
-
-Example of a figure of one column. 
-\begin{figure}
-\begin{center}
-	\includegraphics[width=0.99\columnwidth]{example-figure}
-	\caption{A figure example spanning one column only.\label{fig:label}}   
-\end{center} 
-\end{figure}
-
-Example of a figure spanning two columns. 
-\begin{figure*}
-\begin{center}
-	\includegraphics[width=0.99\textwidth]{example-figure-spanned}
-	\caption{A figure example spanning two columns.\label{fig:label2}}   
-\end{center} 
-\end{figure*}
-
-Example of a table spanning only one column:
 
@@
 
-Example of a table spanning two columns:
-
-\begin{table*}
-\begin{center}
-    \begin{tabular}{ | l | l | l | p{8cm} |}
-    \hline
-    Day & Min Temp & Max Temp & Summary \\ \hline
-    Monday & 11C & 22C & A clear day with lots of sunshine.  
-    However, the strong breeze will bring down the temperatures. \\ \hline
-    Tuesday & 9C & 19C & Cloudy with rain, across many northern regions. Clear spells
-    across most of Scotland and Northern Ireland,
-    but rain reaching the far northwest. \\ \hline
-    Wednesday & 10C & 21C & Rain will still linger for the morning.
-    Conditions will improve by early afternoon and continue
-    throughout the evening. \\
-    \hline
-    \end{tabular}
-\end{center}    
-\end{table*}
-
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions and Future Work}
-Present the main conclusions of the work as well as some future directions for other people interested in continuing this work.
 

### 2013-11-17 Printer_Ballistics.tex
Solution...

@@
 That is, any line printed by this printer model will have basically the same characteristics, regardless of their vertical location in the sheet of paper.
+Page printers, instead, do not print documents line by line.
+In this case, an image of the entire page is ''printed'' on the photoreceptor drum by a laser unit.
+This image attracts toner particles, and then transfers it to the paper sheet.
+Finally a fuser unit heats the paper, so the toner melts and attach it.
+Figure \ref{fig:page_printer} shows a default page printer schema.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{page_printer}
+	\caption{Default page printer schema~\cite{Document_Analysis}.}
+\label{fig:page_printer}   
+\end{center} 
+\end{figure}
 
@@
 \begin{table}
+\caption{Printers used in this work}
 \begin{center}

### 2013-11-19 Printer_Ballistics.tex
Update Printer_Ballistics.tex
Atualizado abstract e Introduction.
Reescrito algumas partes e feito algumas correções.

@@
 \begin{abstract}
-We describe a technique for ballistics of printed documents, that is, link a printed document to a especific printer.
-The principle of this technique is the analysis of character's texture, extracting some properties from the characters of printed and scanned documents, and relate this properties through a co-occurence matrix.
-This matrix can be used to create a "fingerprint" of characters (and related printers), that allows identify a specific printer device that print these characters.
+We describe a technique for ballistics of printed documents, that is, link a printed document to a specific printer.
+The principle of this technique is the analysis of character's texture, by extracting some properties from the characters of the scanned images from the printed documents, and relate this properties through a co-occurrence matrix.
+This matrix can be used to create a "fingerprint" for the characters related to the same printer, what allows us to identify the specific printer device that printed these characters.
 \end{abstract}
@@
 In August of 2013, a russian man wrote his own small print in a credit card contract~\cite{RT}.
-The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the documents.
+The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the document.
 The changes included unlimited credit line, 0 percent interest rates and no fees.
-When the bank decided to terminate man's credit card, because overdue payments, he sued they for more than 24 million rubles (US\$ 727.000).
-How the bank could prove the falsification?
+When the bank decided to terminate the man's credit card, because overdue payments, he sued them for more than 24 million rubles (US\$ 727.000).
+How could the bank prove the falsification?
 
-Altough we are living in a digital era, printed documents still are significant part of our daily.
+Altough we are living in a digital era, printed documents still are a significant part of our day by day.
 Likewise, with the constant reduction in prices and increase in quality of printing equipment, forgeries become increasingly commonplace.
 
-Legal aspects aside, a way to verify if a document, or a part of it, came from a specific device can be character's texture analysis.
+Legal aspects aside, a way to verify if a document, or a part of it, came from a specific device can be through  character's texture analysis.
 
-Our approach for the analysis of character's texture made up as follows.
+Our approach for the analysis of character's texture is as follows.
 From printed pages scanned at high resolution, selected characters were extracted.
-From these characters, we obtained its properties of contrast, correlation, energy and homogeneity, creating with them an co-occurrence matrix.
+From these characters, we obtained its properties of contrast, correlation, energy and homogeneity, creating with them a co-occurrence matrix.
 This matrix can be called a ''fingerprint'' of the character.

### 2013-11-19 Printer_Ballistics.tex
Adicionada imagem do documento

@@
 \section{State-of-the-Art}
-Here goes the state-of-the-art research (talk about prior work for solving the same problem).
+Related work: \cite{Bulan}
 
@@
 Our solution consist in getting the image of characters selected from scanned documents in grayscale, extract its properties of contrast, correlation, energy and homogeneity - creating a co-occurrence matrix - and cluster them by machine learning algorithms.
+
+\subsection{Printers dataset}
+
+The documents used for this work were obtained from the Wikipedia site~\cite{Wikipedia}, and were written in English, some of them containing pictures, some not.
+They were printed by printers listed in Table \ref{tab:printers}.
+
+\begin{table}
+\label{tab:printers}
+\caption{Printers used in this work}
+\begin{center}
+\begin{tabular}{l*{2}{c}r}
+Printer           & Documents \\
+\hline
+Brother-HL4070CDW & 28 \\
+Canon-D1150 & 28 \\
+Canon-MF3240 & 28 \\
+Canon-MF4370DN & 28 \\
+HP-CLJ-CP2025A & 28 \\
+HP-CLJ-CP2025B & 28 \\
+HP-JL-CP1518 & 28 \\
+Lexmark-E260D & 28 \\
+OKI-C330 & 28 \\
+Samsung-CLP315 & 28 \\
+\end{tabular}
+\end{center}
+\end{table}
+
+These documents were scanned at high resolution and saved as Tiff file format (Tagged Image File Format), forming a database.
+These files were made available through an FTP site~\cite{Printers_dataset}.
+An example of a typical document used in this study can be seen in Figure \ref{fig:document}.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{document}
+	\caption{Typical document used in this work~\cite{Wikipedia}.}
+\label{fig:document}   
+\end{center} 
+\end{figure}
 
@@
 
-\begin{table}
-\caption{Printers used in this work}
-\begin{center}
-\begin{tabular}{l*{2}{c}r}
-Printer           & Documents \\
-\hline
-Brother-HL4070CDW & 28 \\
-Canon-D1150 & 28 \\
-Canon-MF3240 & 28 \\
-Canon-MF4370DN & 28 \\
-HP-CLJ-CP2025A & 28 \\
-HP-CLJ-CP2025B & 28 \\
-HP-JL-CP1518 & 28 \\
-Lexmark-E260D & 28 \\
-OKI-C330 & 28 \\
-Samsung-CLP315 & 28 \\
-\end{tabular}
-\end{center}
-\end{table}
-
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-11-19 Printer_Ballistics.tex
mais edição...

@@
 
+\subsection{Characters}
+
 The characters chosen for this work were "e" and "t", both in lowercase, because they are, respectively, the first and second most common letters in texts written in English~\cite{Letter_Frequency}.
+
+\subsection{Printers}
 
@@
 
+By working in this way, page printers do not maintain a characteristic pattern that is repeated line by line across the printed sheet of paper.
+Due to small imperfections that may exist in the photoreceptor drum, each print area generated by this type of device can present different characteristics.
+Taking into account this fact, it was necessary to obtain characters from different parts of the scanned document.
+Basically, each document has roughly divided into three parts: upper, middle, and bottom.
+The Figure \ref{fig:document_areas} shows an example of a document divided in this way.
+If this article is being viewed in color, the upper part of the figure is in red, the middle, in green and bottom, in blue.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{document_areas}
+	\caption{Division of the scanned document in areas.}
+\label{fig:document_areas}   
+\end{center} 
+\end{figure}
+
+Despite showing subtle differences between characters located in different areas of the printout, the print device maintains certain intrinsic characteristics unchanged in all printed characters.
+Such characteristics can be compared to our fingerprints, making it a way to link a printed character to a particular device.
+
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-11-19 Printer_Ballistics.tex
mais edição...

@@
 We describe a technique for ballistics of printed documents, that is, link a printed document to a specific printer.
-The principle of this technique is the analysis of character's texture, by extracting some properties from the characters of the scanned images from the printed documents, and relate this properties through a co-occurrence matrix.
+The principle of this technique is the analysis of character's texture, by extracting some properties from the characters of scanned images from the printed documents, and relate this properties through a co-occurrence matrix.
 This matrix can be used to create a "fingerprint" for the characters related to the same printer, what allows us to identify the specific printer device that printed these characters.
@@
 
-These documents were scanned at high resolution and saved as Tiff file format (Tagged Image File Format), forming a database.
+These printed documents were scanned at high resolution and saved as Tiff file format (Tagged Image File Format), forming a database.
 These files were made available through an FTP site~\cite{Printers_dataset}.
@@
 
+To avoid inconsistencies and / or values "off the curve", we used only characters printed in the same font and size, for all printers.
+With the same objective, we used only characters printed in normal font, not analyzing characters in bold, italic, underline, strikeout, superscript, subscript, or any other form of letter change.
+
+Were not considered characters from misaligned documents, i.e. characters from apparently obliquely scanned documents.
+
 \subsection{Printers}
@@
 This is a crucial difference, and should be considered for more careful study.
+
 Line printers print documents line by line from the top of the sheet, keeping a characteristic pattern which periodically repeats for each paper feed.
-That is, any line printed by this printer model will have basically the same characteristics, regardless of their vertical location in the sheet of paper.
+That is, any line printed by this printer model will have basically the same characteristics, regardless of their vertical location in the paper sheet.
+
 Page printers, instead, do not print documents line by line.
@@
 This image attracts toner particles, and then transfers it to the paper sheet.
-Finally a fuser unit heats the paper, so the toner melts and attach it.
+Finally, a fuser unit heats the paper, so the toner melts and attach it.
 Figure \ref{fig:page_printer} shows a default page printer schema.
@@
 
-By working in this way, page printers do not maintain a characteristic pattern that is repeated line by line across the printed sheet of paper.
+By working in this way, page printers do not maintain a characteristic pattern that is repeated line by line across the printed paper sheet.
 Due to small imperfections that may exist in the photoreceptor drum, each print area generated by this type of device can present different characteristics.
 Taking into account this fact, it was necessary to obtain characters from different parts of the scanned document.
+
 Basically, each document has roughly divided into three parts: upper, middle, and bottom.

### 2013-11-19 Printer_Ballistics.tex
mais edição...

@@
 \section{Introduction}
+\label{sec:introduction}
+
 In August of 2013, a russian man wrote his own small print in a credit card contract~\cite{RT}.
@@
 \section{State-of-the-Art}
+\label{sec:state_of_the_art}
+
 Related work: \cite{Bulan}
@@
 \section{Proposed Solution}
+\label{sec:proposed_solution}
 
@@
 \subsection{Printers dataset}
+\label{subsec:printers_dataset}
 
@@
 \subsection{Characters}
+\label{subsec:characters}
 
@@
 
-Were not considered characters from misaligned documents, i.e. characters from apparently obliquely scanned documents.
+Were not considered characters from misaligned documents, i.e.
+characters from apparently obliquely scanned documents.
+Figure \ref{fig:characters} shows examples of two characters obtained from scanned documents, one of them being usable and the other not, being considered rotated.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{characters}
+	\caption{Examples of characters: the left one was considered useful; the right one, slightly rotated.}
+\label{fig:characters}   
+\end{center} 
+\end{figure}
+
+Subsection \ref{subsec:co-occurence_matrix} will be explained in more detail why not use rotated characters.
 
 \subsection{Printers}
+\label{subsec:printers}
 
@@
 
+\subsection{Gray level co-occurence matrix}
+\label{subsec:co-occurence_matrix}
+
+Co-occurrence matrix is a tabulation of how many different combinations of intensity values of pixels (grayscale) occur in an image.
+The primary use of the co-occurrence matrix is characterized texture in an image from a set of statistics for instances of
+each gray level in different pixels along different directions~\cite{Rocha}.
+
+Co-occurrence matrix considers the relationship between two pixels at a time, one called as ''reference pixel'' and another as ''neighbor pixel''.
+The neighboring pixel chosen can be neighbor in any direction: east (right), west (left), north (above), south (below), or diagonally, i.e.
+northeast, northwest, southwest and southeast of each reference pixel.
+Also the neighborhood need not be exactly one pixel, can be 2, 3, or any value.
+Each pixel within the image becomes the reference pixel, starting at the top left and proceeding to the lower right.
+There will be particular cases.
+For instance, pixels of the right margin of the image does not have neighboring right.
+
+Co-occurrence, in its most general form, can be specified by a matrix of relative frequencies $P (i, j, d,\theta)$, where two neighboring texture elements separated by a distance $d$ in a direction $\theta$ occur in the image, one with the property $i$ and another with property $j$.
+
+From a co-occurrence matrix can be obtained some properties of the analyzed image.
+For this work, we used the properties of contrast, correlation, energy and homogeneity to create a fingerprint of the printed characters.
+
+Using an example similar to the rotated character, we can compare the value differences in the properties obtained from the co-occurrence matrix (Figure \ref{fig:characters_angle}).
+In this case, the character on the left was obtained directly from the scanned document, the character on the right is the same character, but rotated -4º.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{characters_angle}
+	\caption{On the left, a character obtained from a scanned document and to the right, the same character, rotated -4º.}
+\label{fig:characters_angle}   
+\end{center} 
+\end{figure}
+
+Table \ref{tab:properties_differences} lists the differences between the properties of the character sample obtained from the co-occurrence matrix.
+
+\begin{table}
+\label{tab:properties_differences}
+\caption{Differences between an original character and a rotated character.}
+\begin{center}
+\begin{tabular}{l*{3}{c}r}
+Property & Original character & Rotated character (-4º) \\
+\hline
+Contrast & 3.2443 - 2.2905 & 5.1617 - 4.6504 \\
+Correlation & 0.7869 - 0.8502 & 0.6967 - 0.7264 \\
+Energy & 0.1608 - 0.1744 & 0.1106 - 0.1216 \\
+Homogeneity & 0.6946 - 0.7462 & 0.6610 - 0.6995 \\
+\end{tabular}
+\end{center}
+\end{table}
+
+As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values ​​obtained from the co-occurrence matrix.
+
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-11-19 Printer_Ballistics.tex
Iniciando Related works

@@
 
-Related work: \cite{Bulan}
+Related work: \cite{Bulan} \cite{Printer_Profiling}.
 
@@
 
-As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values ​​obtained from the co-occurrence matrix.
+As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values obtained from the co-occurrence matrix.
 

### 2013-11-19 Printer_Ballistics.tex
Related works

@@
 
-Related work: \cite{Bulan} \cite{Printer_Profiling}.
+Literature on the identification of printing devices from their printed documents is not wide in Academia.
+The work of Kee et al \cite{Printer_Profiling} reports a technique of geometric modeling of degradation caused by the printer.
+According to the authors, this degradation, measured based on a character basis, is modeled constructing a linear basis from characters commonly found on a printed page.
+From the point of view of ballistics, the accuracy of the developed technique allows to identify the device that originated the printed pages.
+According to the authors, the technique allows to distinguish between printers of different brands and models, but not among printers of the same make and model.
+
+The work Bulan et al \cite{Bulan} demonstrates a technique for analyzing geometric distortions introduced during the printing process of electrophotographic printers (EP).
+According to the authors, it is first determined the geometric distortion signature to the printer using only printed pages.
+It is then built up a database and the printer used to print a test page is identified by computing the geometric distortion signature from the printed test page and correlated it with the signatures present in the database.
+Geometric distortion signature is calculated comparing dot positions extracted from the printed image and estimated dot positions before printing.
+
+Valuable is also the work of Rocha and Leite \cite{Rocha}.
+This work deals with the concept of analysis of textures through the co-occurrence matrix, used as a cornerstone of the solution proposed by us.
 

### 2013-11-19 Printer_Ballistics.tex
Related works

@@
 Literature on the identification of printing devices from their printed documents is not wide in Academia.
-The work of Kee et al \cite{Printer_Profiling} reports a technique of geometric modeling of degradation caused by the printer.
+The work of Kee and Farid \cite{Printer_Profiling} reports a technique of geometric modeling of degradation caused by the printer.
 According to the authors, this degradation, measured based on a character basis, is modeled constructing a linear basis from characters commonly found on a printed page.
@@
 
-Valuable is also the work of Rocha and Leite \cite{Rocha}.
-This work deals with the concept of analysis of textures through the co-occurrence matrix, used as a cornerstone of the solution proposed by us.
+The work of Pollard et al \cite{Pollard} presents a general method for extracting a signature print from the outer boundary of a text glyph.
+
+Valuable is also the work of Rocha and Leite \cite{Rocha}. This work deals with the concept of analysis of textures through co-occurrence matrix, used as a cornerstone of the solution proposed by us.
 
@@
 Using an example similar to the rotated character, we can compare the value differences in the properties obtained from the co-occurrence matrix (Figure \ref{fig:characters_angle}).
-In this case, the character on the left was obtained directly from the scanned document, the character on the right is the same character, but rotated -4º.
+In this case, the character on the left was obtained directly from the scanned document; character on the right is the same character, but rotated -4º.
 
@@
 \section{Experiments and Discussion}
-
+\label{sec:experiments}
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions and Future Work}
+\label{sec:conclusions}
+
+\section{Acknowledgements}
+\label{sec:acknownledgements}
+
+We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.
 

### 2013-11-28 Printer_Ballistics.tex
Experiments

@@
 %%% Title and authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\title{Printer ballistics through character's texture analysis}
+\title{Printer ballistics through texture analysis of characters}
 \author{Adriano Ruggero\thanks{Institute of Computing, University of Campinas (Unicamp). \textbf{Contact}: \tt\small{arruggero@lasca.ic.unicamp.br}}\\
@@
 HP-CLJ-CP2025A & 28 \\
-HP-CLJ-CP2025B & 28 \\
 HP-JL-CP1518 & 28 \\
@@
 \label{sec:experiments}
+
+As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the proprieties would be extracted.
+With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution.
+In the first instance, we needed to determine the best options for classifying the characters and attributing them to a Printer.
+But our final goal is not to attribute the characters to a printer, but a whole document, so in the next step, we propose a way of attributing the printer based on the classification of the characters.
+
+\subsection{Characters Selection and Proprieties Extraction}
+
+First we selected three characters from each one of the three sections from a document, and repeated that for all documents.
+There were 3x3x28 = 252 characters selected for each printer, what gave us a total of 1512.
+
+For the proprieties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}.
+From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character.
+The second one gave us four per type, in other words, a sixteen sized vector.
+
+\begin{figure}
+\begin{center}
+	\includegraphics[width=0.99\columnwidth]{neighbor}
+	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest)}
+\label{fig:neighbor}   
+\end{center} 
+\end{figure}
+
+\subsection{Characters Classification}
+
+The just acquired descriptors are used for evaluation the available classification algorithms.
+For this evaluation it was separated 66\% of the chars to be used as training (1008) and the rest for testing (504).
+From them we separate the most prominent and present the results in table \ref{tab:correct_classification}.
+
+\begin{table}
+\label{tab:correct_classification}
+\caption{Percentage of correct classifications of printers.}
+\begin{center}
+\begin{small} 
+\setlength{\tabcolsep}{3pt} 
+\begin{tabular}{l*{5}{c}r} & \multicolumn{2}{c}{Neighborhood A} & \multicolumn{2}{c}{Neighborhood B}\\ \cline{1-5}
+Method & Chars e’s & Chars t’s & Chars e’s & Chars t’s \\
+\hline
+Logistic & 81 & 81.3 & 85 & 84.6\\
+KStar & 77.6 & 83 & 72 & 79.6\\
+RotationForest & 83.1 & 85 & 81.7 & 85.7\\
+NNge & 74.1 & 80.2 & 72.2 & 67.8\\
+LMT & 83.8 & 84.6 & 82.7 & 85.5\\
+
+\end{tabular}
+\end{small}
+\end{center}
+\end{table}
+
+Analyzing the results we can see a slightly better classification on the characters ''t'', perhaps they are more unique for each printer.
+The results also show that using a neighborhood of four pixels for many cases made the classification worst, what was against our intuition since its descriptors were longer than of the other neighborhood we used.
+
+\subsection{Printer Attribution}
+
+As said before, attributing a printer to the character is not the main objective, so it was necessary to define a logical output from the classified characters obtained in the previous step.
+For this purpose we choose to attribute a document to the printer that had most classified characters on it.
+
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2013-11-28 Printer_Ballistics.tex
Fumada do Gabriel

@@
 \usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
+\usepackage{appendix}
 \input{abaco}
@@
 
-\begin{table}
+\begin{table*}
+\caption{Printers used in this work}
 \label{tab:printers}
-\caption{Printers used in this work}
 \begin{center}
-\begin{tabular}{l*{2}{c}r}
-Printer           & Documents \\
+    \begin{tabular}{ | c | c | c | c |}
     \hline
-Brother-HL4070CDW & 28 \\
-Canon-D1150 & 28 \\
-Canon-MF3240 & 28 \\
-Canon-MF4370DN & 28 \\
-HP-CLJ-CP2025A & 28 \\
-HP-JL-CP1518 & 28 \\
-Lexmark-E260D & 28 \\
-OKI-C330 & 28 \\
-Samsung-CLP315 & 28 \\
+Printer & Documents & Characters ''e'' & Characters ''t'' \\ \hline
+Brother-HL4070CDW & 28 & 252 & 252\\
+Canon-D1150 & 28 & 252 & 252\\
+Canon-MF3240 & 28 & 252 & 252\\
+Canon-MF4370DN & 27 & 252 & 252 \\
+HP-CLJ-CP2025A & 28 & 250 & 250\\
+HP-JL-CP1518 & 0 & 0 & 0\\
+Lexmark-E260D & 0 & 0 & 0\\
+OKI-C330 & 0 & 0 & 0\\
+Samsung-CLP315 & 0 & 0 & 0 \\
+\hline
     \end{tabular}
 \end{center}    
-\end{table}
+\end{table*}
 
@@
 	\includegraphics[width=0.99\columnwidth]{neighbor}
-	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest)}
+	\caption{Neighborhood A, leftmost, and B, rightmost, used in properties extraction (the darker pixel is the pixel-of-interest).}
 \label{fig:neighbor}   
@@
 
+\appendix
+
 \end{document}

### 2013-11-28 Printer_Ballistics.tex
Appendix
Before lunch

@@
 
+Details on how to calculate values of contrast, correlation, energy and homogeneity can be seen in Appendix A.
+
 %%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \appendix
+\label{app:Appendix A}
+
+\section{Formulas}
+\subsection{Contrast}
+
+Returns the measure of contrast between the pixel of interest and neighboring pixel. For a constant image (same shade of gray to the full extent) the value is 0.
+
+$$\sum_{i,j}\vert i - j \lvert^2 p(i,j)$$
+
+\subsection{Co-relation}
+
+Returns the measure of how much the pixel is related to its neighbor. The range is from -1 to 1, where 1 means a fully correlated and -1, totally uncorrelated image.
+
+$$\sum_{i,j} \frac{(i - \mu i) (j - \mu j) p(i,j)} {\sigma_i \sigma_j}$$
+
+\subsection{Energy}
+
+Returns the sum of squared raised elements within the array. The range of possible values is from 0 to 1. A constant image (same shade of gray in all its extension) has value 1.
+
+$$\sum_{i,j} p(i, j)^2$$
 

### 2013-11-28 Printer_Ballistics.tex
After lunch

@@
 HP-CLJ-CP2025A & 28 & 250 & 250\\
-HP-JL-CP1518 & 0 & 0 & 0\\
-Lexmark-E260D & 0 & 0 & 0\\
-OKI-C330 & 0 & 0 & 0\\
-Samsung-CLP315 & 0 & 0 & 0 \\
+Lexmark-E260D & 30 & 636 & 629\\
 \hline
@@
 
+\newpage
+
 \appendix
@@
 \section{Formulas}
+
+$p$ represents the pixel-of-interest.
+
+$i$ and $j$ represents the positions of the values of the co-occurrence matrix.
+
+$\mu i$ and $\mu j$ represents the mean of $i$ and $j$, respectively.
+
+$\sigma i$ and $\sigma j$ represents the standard deviation of $i$ and $j$, respectively.
+
 \subsection{Contrast}
@@
 
+\subsection{Homogeneity}
+
+Returns a value that represents the relative proximity of the diagonal elements of the co-occurrence matrix.
+The range of possible values is between 0 and 1, and the value 1 represents a diagonal matrix.
+
+$$\sum_{i,j} \frac{p(i, j)}{1 + \vert i - j \lvert}$$
+
 \end{document}

### 2013-11-28 Printer_Ballistics.tex
Before presentation starts
Quase

@@
 \input{abaco}
-
+\makeatletter
 \cvprfinalcopy % *** Uncomment this line for the final submission
@@
 
-Our solution consist in getting the image of characters selected from scanned documents in grayscale, extract its properties of contrast, correlation, energy and homogeneity - creating a co-occurrence matrix - and cluster them by machine learning algorithms.
+Our solution consist in getting the image of characters selected from scanned documents in grayscale, create a co-occurrence matrix, extract its properties of contrast, correlation, energy and homogeneity - creating a feature vector - and cluster them by machine learning algorithms.
 
@@
 
-As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the proprieties would be extracted.
+As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the properties would be extracted.
 With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution.
@@
 
-\subsection{Characters Selection and Proprieties Extraction}
+\subsection{Characters Selection and Properties Extraction}
 
@@
 
-For the proprieties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}.
+For the properties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}.
 From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character.
@@
 
-$i$ and $j$ represents the positions of the values of the co-occurrence matrix.
+$i$ and $j$ represents the value of the properties.
 
@@
 
+\section{Features vectors}
+
+\subsection{Training set}
+
+Figure \ref{fig:feature_vector} shows a portion of the file with the feature vectors for training the classifiers.
+
+\begin{figure*}
+\begin{center}
+	\includegraphics[width=2\columnwidth]{feature_vector}
+	\caption{Feature vector for training.}
+\label{fig:feature_vector}   
+\end{center} 
+\end{figure*}
+
+Figure \ref{fig:validation} shows a portion of the file with the feature vectors for validation.
+
+\begin{figure*}
+\begin{center}
+	\includegraphics[width=2\columnwidth]{validation}
+	\caption{Feature vector for validation.}
+\label{fig:validation}   
+\end{center} 
+\end{figure*}
+
 \end{document}

### 2013-11-29 Printer_Ballistics.tex
Corrigidas as tabelas
Mais tabelas

@@
 \begin{table}
+\caption{Differences between an original character and a rotated character.}
 \label{tab:properties_differences}
-\caption{Differences between an original character and a rotated character.}
 \begin{center}
@@
 As a starting point for our experiments, it was necessary to select the desired characters from the documents on which the properties would be extracted.
-With the extracted proprieties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution.
+With the extracted properties of contrast, correlation, energy and homogeneity from the characters, we started evaluating the best methodology and machine learning algorithms for our solution.
 In the first instance, we needed to determine the best options for classifying the characters and attributing them to a Printer.
-But our final goal is not to attribute the characters to a printer, but a whole document, so in the next step, we propose a way of attributing the printer based on the classification of the characters.
+But our final goal is not to attribute the characters to a printer, but a whole document, so, in the next step, we propose a way of attributing the printer based on the classification of the characters.
 
@@
 For the properties extraction we used two different neighborhoods show in figure \ref{fig:neighbor}.
-From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a vector of descriptors of eight values for a character.
+From the first neighborhood we gathered two characteristics per type (contrast, correlation, energy and homogeneity), originating a feature vector of eight values for a character.
 The second one gave us four per type, in other words, a sixteen sized vector.
@@
 
-The just acquired descriptors are used for evaluation the available classification algorithms.
+The just acquired features are used for evaluation the available classification algorithms.
 For this evaluation it was separated 66\% of the chars to be used as training (1008) and the rest for testing (504).
@@
 \begin{table}
+\caption{Percentage of correct classifications of printers.}
 \label{tab:correct_classification}
-\caption{Percentage of correct classifications of printers.}
 \begin{center}
@@
 
-Analyzing the results we can see a slightly better classification on the characters ''t'', perhaps they are more unique for each printer.
-The results also show that using a neighborhood of four pixels for many cases made the classification worst, what was against our intuition since its descriptors were longer than of the other neighborhood we used.
+Analyzing the results we can see a slightly better classification on the characters ''t'' (perhaps they are more unique for each printer).
+The results also show that using a neighborhood of four pixels, for many cases, made the classification worst, what was against our intuition, since its descriptors were longer than of the other neighborhood we used.
 
@@
 As said before, attributing a printer to the character is not the main objective, so it was necessary to define a logical output from the classified characters obtained in the previous step.
-For this purpose we choose to attribute a document to the printer that had most classified characters on it.
+For this purpose we choose to attribute a document to the printer that had most classified characters on the document sample of characters.
+
+Since there were no significant difference between Neighborhoods A and B, we tested using only the first.
+For this tests it were separated 4 documents per printer, 24 in total, and the rest of the documents were used for training.
+We choose to use only the three classifier methods that had the best results in characters classification.
+The printer attribution results are present in table \ref{tab:correct_printer_attribution}.
+
+\begin{table}
+\caption{Percentage of correct printer attribution.}
+\label{tab:correct_printer_attribution}
+\begin{center}
+\begin{small} 
+\setlength{\tabcolsep}{3pt} 
+\begin{tabular}{l*{4}{c}r} \cline{1-4}
+Method & Chars e’s & Chars t’s & Chars e’s and t’s \\
+\hline
+Logistic & 21/24 = 87.5\% & 22/24 = 91.7\% & 21/24 = 87.5\% \\
+
+RotationForest & 21/ 24 = 87.5\% & 21/24 = 87.5\% & 22/24 = 91.7\% \\
+
+LMT & 21/24 = 87.5\% & 21/24 = 87.5\% & 22/24 = 91.7\% \\
+
+\end{tabular}
+\end{small}
+\end{center}
+\end{table}
+
+Again, it is shown that using only characters ''e'' or only characters ''t'' we have almost the same correct classification rate.
+If we combine the two characters classification and use it for attribution there is a small improvement on the results.
 
@@
 \label{sec:conclusions}
+
+In this article we have described a technique for printer attribution based on the properties extracted from the character’s texture of a document.
+These properties were contrast, correlation, energy and homogeneity, and could be used to create a signature for the printer that generated the document.
+
+The feature vector size, formed by these properties, varies depending on the neighborhood defined for the generation of the Co-occurrence matrix.
+In the experiments made we used two different neighborhoods, and it was shown that a greater feature vector doesn’t mean we will have a better classifier.
+Still, there is room for more tests in this aspect, experiments with other neighborhoods size and in different directions must be done for identifying the best parameters.
+Another consideration that can be taken in account is if all properties extracted from the co-occurrence matrix should be used, perhaps different combinations of them can bring better results.
+
+For the experiments done, we used only the characters ''e'' and ''t''.
+Anyhow, the results made us believe that the character choice would have probably low impact on the results obtained, since in some methods for classification there is a higher accuracy and for others a lower when we alternate between ''e'' and ''t''.
+What can have a better impact is the number of characters selection from each part of the document (we picked only a small portion of them).
+
+Our work presents an unexplored characteristic from the printers uniqueness printing process that can be extracted afterwards with the scanned documents created on them.
+It was also shown that this characteristic can be used in ballistics for printer attribution but that still needs further investigation and experiments on the best methodology for achieving optimal results.
 

### 2013-11-29 Printer_Ballistics.tex
Artigo finalizado

@@
 
+Another direction can also be made using other texture analyzers, such as HOG (Histograms of Oriented Gradients Extract) or LBP (Local Binary Patterns), and no GLCM.
+
 Our work presents an unexplored characteristic from the printers uniqueness printing process that can be extracted afterwards with the scanned documents created on them.
 It was also shown that this characteristic can be used in ballistics for printer attribution but that still needs further investigation and experiments on the best methodology for achieving optimal results.
+
+Although not the purpose of this study, and future studies, manual extraction of characters is still a counterproductive way of working.
+Develop a (semi) automated method would be of great benefit to researchers in this field.
 
@@
 
-We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.
+We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student, Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.
 

### 2013-11-29 Printer_Ballistics.tex
Artigo finalizado de novo

@@
 Canon-MF4370DN & 27 & 252 & 252 \\
-HP-CLJ-CP2025A & 28 & 250 & 250\\
-Lexmark-E260D & 30 & 636 & 629\\
+HP-CLJ-CP2025A & 28 & 252 & 252\\
+Lexmark-E260D & 28 & 252 & 252\\
 \hline
@@
 Although not the purpose of this study, and future studies, manual extraction of characters is still a counterproductive way of working.
-Develop a (semi) automated method would be of great benefit to researchers in this field.
+Develop a (semi) automated method to do this would be of great benefit to researchers in this field.
 
